Tree height and hydraulic traits shape growth responses across droughts in a temperate broadleaf forest

### 2020-07-18 manuscript/tables&figures.Rmd
new fig 4
#71

![**Figure 4_option1. Visualization of best model for all droughts combined.** Model coefficients are given in Table S6.** ](tables_figures/publication/best_model_with_data.png){width=500px}

![**Figure 4_option 2. Visualization of best model for all droughts combined and for each drought separately.** Model coefficients are given in Table S6. **confidence intervals would be added.** ](tables_figures/publication/best_models_ind_years.png){width=500px}

>>>>

![**Figure 4_option1. Visualization of best model for all droughts combined.** Model coefficients are given in Table S6.** ](tables_figures/publication/Figure4_model_vis.png){width=500px}
